Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-07 R0V0.tex
Minor change

\mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		\arg(Y_{ij})\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ indexed by the set $\mathscr{K}(k)$.

@@

\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N\dfrac{N+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

@@

\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} leads to the following components of the matrix $W$ for system~\eqref{eq:example} with four agents lead to the

>>>>

\mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		\arg(Y_{ij}(\cdot,u))\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ indexed by the set $\mathscr{K}(k)$.

@@

\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

@@

\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual},  the solver took 23 seconds to compute the matrix $W$ for system~\eqref{eq:example} with four agents lead to the
